---
title: "Exercise_b_3"
output: html_document
author: Silvan Vollmer
date: 20.09.21
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1. b)

Create an HTML document that samples 100 values from a log-normal distribution (say, mu=1, sigma=.25); create a histogram of the distribution and the distribution on the log scale; report the mean and variance of the sample in line in the text. In general, do not just dump the R code and plots in the HTML document; break your exercises into sections with headings, add some text and make it readable.


#Code for Data Generation

```{r}
set.seed(10) #for reproducibility
data <- rlnorm(n=100,   meanlog = 1,sdlog = .25)
```
#Code for Histograms

```{r}
hist(data,main = "Histogram of simulated data")
hist(log(data),main = "Histogram of simulated data on log scale")
```

#Code for Summary Statistics

```{r}
mean_data <- mean(data)
var_data <- var(data)
mean_data_log <- mean(log(data))
var_data_log <- var(log(data))
```

# Results

The mean of the simulated data is `r mean_data`, the variance is `r var_data`.
The mean of the simulated log-data is `r mean_data_log`, the variance is `r var_data_log`.



